A Heuristic Approach towards Drawings of Graphs with High Crossing Resolution

### 2018-06-05 paper/paper.tex
improving a bit the presentation

In the remainder of this section, we discuss some interesting variants of our~algorithm, which are motivated by the following preliminary observations that we made from the computed layouts: Drawings with good crossing resolution tend to have bad aspect ratio (that is, the ratio of the longest to the shortest edge is large) and poor angular resolution (that is, the angles formed by adjacent edges are small). The former seems to be a consequence of the fact that drawings with good crossing resolution tend to be quite demanding in area. The later can easily become clear by a simple example; if in a drawing all edges are either almost horizontally or almost vertically drawn, then while its crossing resolution is $\epsilon$-close to $90^\circ$, its angular resolution is $\epsilon$-close to~$0^\circ$.

@@

\myparagraph{Total resolution} 
%
The notion of the total resolution of a drawing was relatively recently introduced with aim of ``balancing'' the measures of the crossing and of the angular resolution of a drawing~\cite{DBLP:journals/cj/ArgyriouBS13}. Formally, it is defined as the minimum of these two measures. It was not difficult to adjust our algorithm to yield drawings with high total resolution by simply taking into account also the angular resolution of the drawing. In particular, if the total resolution of the drawing is defined by its angular resolution, then the way we compute the critical vertices of this drawing has to change; the critical vertices must be the endvertices of the pairs of edges that define the angular resolution. Also, at each iteration of our algorithm we have to ensure that the total resolution does not decrease. We do so by simply rejecting candidate positions, which yield a reduced total resolution.

>>>>

In the remainder of this section, we discuss some interesting variants of our~algorithm, which are motivated by the following preliminary observations that we made from the computed layouts: Drawings with good crossing resolution tend to have bad aspect ratio (that is, the ratio of the longest to the shortest edge is large) and poor angular resolution (that is, the angles formed by adjacent edges are small). The former seems to be a consequence of the fact that drawings with good crossing resolution tend to be quite demanding in area. The later can easily become clear by an example; if in a drawing all edges are either almost horizontally or almost vertically drawn, then the crossing resolution of this drawing is arbitrarily close to $90^\circ$, while its angular resolution is arbitrarily close to~$0^\circ$.

@@

\myparagraph{Total resolution} 
%
The notion of the total resolution of a drawing was introduced relatively recently with aim of ``balancing'' the measures of the crossing and of the angular resolution of a drawing~\cite{DBLP:journals/cj/ArgyriouBS13}. Formally, it is defined as the minimum of these two measures. It was not difficult to adjust our algorithm to yield drawings with high total resolution by simply taking into account also the angular resolution of the drawing. In particular, if the total resolution of the drawing is defined by its angular resolution, then the way we compute the critical vertices of this drawing has to change; the critical vertices must be the endvertices of the pairs of edges that define the angular resolution. Also, at each iteration of our algorithm we have to ensure that the total resolution does not decrease. We do so by simply rejecting candidate positions, which yield a reduced total resolution.
